Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-05 notes.tex
the Greens functions dont seem to match up, most probably because of the dissimilar n=1(3) sectors. Scrape this approach.

\begin{equation}\begin{aligned}
	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
		    &&.&&\\
		    &&.&&\\
		    &&.&&\\
\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
		g_1 & g_0 & g_1 & ... & ...\\
		... & g_1 & g_0 & g_1 & ... \\
		    &&...&&\\
		    &&...&&\\
\end{pmatrix} 
\end{aligned}\end{equation}
It can be written in the operator form as
\begin{equation}\begin{aligned}
	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
\end{aligned}\end{equation}
We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
\begin{equation}\begin{aligned}
	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice. $q_i$ are the projections of $\vec q$ along those vectors. $a_i$ are the lattice spacings along each primitive vector. Adding the Hermitian conjugate simply extracts the real part:
\begin{equation}\begin{aligned}
	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
The inverse Greens function thus becomes diagonal in momentum space
\begin{equation}\begin{aligned}
G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
	& g_0 + g_1\xi_{\vec k_2} && \\
	&& g_0 + g_1\xi_{\vec k_3} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
\begin{equation}\begin{aligned}
	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
\begin{equation}\begin{aligned}
	G_H(\vec k, \omega) &= g_0 + g_1 \xi_{\vec k}\\
			    &= \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}
\end{aligned}\end{equation}

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
\begin{equation}\begin{aligned}
	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
\end{aligned}\end{equation}
The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t
\end{aligned}\end{equation}
for the first inner product, and
\begin{equation}\begin{aligned}
	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t
\end{aligned}\end{equation}
for the second. The Greens function is therefore
\begin{equation}\begin{aligned}
	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
\end{aligned}\end{equation}
The site local spectral can now be calculated:
\begin{equation}\begin{aligned}
	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
\end{aligned}\end{equation}

\subsection*{Greens functions for Anderson molecule}
\begin{equation}\begin{aligned}
	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{GS} - E_n}\right]\\
	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right]\\
\end{aligned}\end{equation}

>>>>

\begin{equation}\begin{aligned}
	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
		    &&.&&\\
		    &&.&&\\
		    &&.&&\\
\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
		g_1 & g_0 & g_1 & ... & ...\\
		... & g_1 & g_0 & g_1 & ... \\
		    &&...&&\\
		    &&...&&\\
\end{pmatrix} 
\end{aligned}\end{equation}
It can be written in the operator form as
\begin{equation}\begin{aligned}
	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
\end{aligned}\end{equation}
We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
\begin{equation}\begin{aligned}
	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice. $q_i$ are the projections of $\vec q$ along those vectors. $a_i$ are the lattice spacings along each primitive vector. Adding the Hermitian conjugate simply extracts the real part:
\begin{equation}\begin{aligned}
	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
The inverse Greens function thus becomes diagonal in momentum space
\begin{equation}\begin{aligned}
G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
	& g_0 + g_1\xi_{\vec k_2} && \\
	&& g_0 + g_1\xi_{\vec k_3} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
\begin{equation}\begin{aligned}
	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
\begin{equation}\begin{aligned}
	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
			    &= \left\{\frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}\right\}^{-1}
\end{aligned}\end{equation}

\section{Why this does not work}
Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
	\xi_{\vec k} = 2, -2
Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Anderson molecule. The inverse of a $2\times 2$ matrix is
	G_A^{-1} = \frac{1}{\text{Det }G_A}\begin{pmatrix} \left(G_A\right)_{zz} &  -\left(G_A\right)_{zd} \\ -\left(G_A\right)_{zd} & \left(G_A\right)_{dd}\end{pmatrix} \implies \begin{cases}
		g_0 = \frac{1}{2} \frac{1}{\text{Det }G_A}\left[\left(G_A\right)_{zz} + \left(G_A\right)_{dd}\right] \\
		g_1 = -\frac{1}{\text{Det }G_A}\left(G_A\right)_{zd} \\
	\end{cases}
The matrix elements of $G_A$ are calculated in the appendix. The actual real space local Greens function for the Hubbard dimer is also shown there. By comparing the Greens functions (for eg., eqs.~\ref{dimer_local_G} and \ref{mole_local_G}), one can see that the structures of the denominators are different. This is because of the fact that the eigenvalues for $n=1$ or $n=3$ of the Hubbard dimer are different from that for the Anderson molecule. This indicates that we need to change the auxiliary system (SIAM with non-interacting zero mode).

@@

The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
\begin{equation}\begin{aligned}
	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
\end{aligned}\end{equation}
The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \mp t
\end{aligned}\end{equation}
for the first inner product, and
\begin{equation}\begin{aligned}
	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
	\left\{ E_n \right\} &= \pm t
\end{aligned}\end{equation}
for the second. The Greens function is therefore
\begin{equation}\begin{aligned}
	\label{dimer_local_G}
	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
\end{aligned}\end{equation}
The site local spectral can now be calculated:
\begin{equation}\begin{aligned}
	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
\end{aligned}\end{equation}

\section*{Appendix: Greens functions for Anderson molecule}
	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
We proceed exactly as before. With the following shorthand notations,
	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
the diagonal Green's functions are
	\label{mole_local_G}
	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
and the off-diagonal Greens functions are
	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
